One-dimensional Classical Gas in a Harmonic Trap with Repulsive Interaction

### 2017-01-20 Zhiyu.tex
Jan20 PRE format, tex

If the oscillating phases of particles are highly correlated, for example, initial state with zero velocity, the shape of cloud will be a thin ellipse. If the phase of oscillation is completely random, the cloud should be isotropic in phase space. In view of this, we defined a shape factor S:
\\$S=\frac{a-b}{a+b}$, where a and b are long axis and short axis of inertia ellipse in phase space respectively. a,b can be calculated by diagonalizing the inertia matrices I: $I_{xx}=\sum{x^2}, I_{xp}=I_{px}=\sum{xp},I_{pp}=\sum{p^2}$
S=1 for line-shape distribution, S=0 for circular distribution.
The time evolution of S will probably show how fast the distribution ``forget" its initial shape.

>>>>

If the oscillating phases of particles are highly correlated, for example, initial state with zero velocity, the shape of cloud will be a thin ellipse. If the phase of oscillation is completely random, the cloud should be isotropic in phase space. In view of this, we defined a shape polarization S:
\\$S=\frac{a-b}{a+b}$, where a and b are long axis and short axis of inertia ellipse in phase space respectively. a,b can be calculated by diagonalizing the inertia matrices I: $I_{xx}=\sum{x^2}, I_{xp}=I_{px}=\sum{xp},I_{pp}=\sum{p^2}$. S=1 for line-shape distribution, S=0 for circular distribution. The time evolution of S will probably show how fast the distribution ``forget" its initial shape.

\begin{figure}
\centering
\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=3000.eps}
\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=20000.eps}
\includegraphics[scale=0.4]{ZhiyuPictures/N=20_shape_F=1000_E=100000.eps}
\caption{N=20, F=1000, E=3000(top), E=20000(middle), E=100000(bottom). All start with initial states S=1. \label{fig:shape}}
\end{figure}

The time evolution of shape polarization S is shown in Fig.\ref{fig:shape}, when E is much lower than the thermalizaion threshold, S decreases to 0.3 in almost no time. On the contrary, when E is much higher than the threshold value, it takes a long time for S to dacay.
